Biomass predictions and VOCC

### 2019-08-06 analysis/VOCC/4-vocc-by-spp.Rmd
get two varible vocc plots working

climate <- "do and temperature"
max_thresholds <- c(Inf, 0.75)
min_thresholds <- c(0.25, Inf)
optimal_value <- c(6.5, 2)
```

@@

optimal_string <- paste0(optimal_value, collapse = "-")
climate_string <- gsub(" ", "-", gsub("\\/", "-", tolower(climate_string)))
```

@@

plot <- gridExtra::grid.arrange(
  vocc_plot_temp, vocc_plot_do,
  ncol = 2,
  top = grid::textGrob(paste(climate, "-", optimal_value, "-",
    min_string,"to", max_string, "-", start_time, "-", delta_t_total, ".rds"))
)

@@

  for (j in seq_along(variable_names)){
  vectors <- vectors %>% filter( paste0("X",j) < (optimal_value[j] - min_thresholds[j]) )
  }

@@

if (length(vectors[ ,2]) == 0) {
  try({other_coefs <- readRDS("data/vocc-by-spp-sdmTMB-coefs.RDS")})

  coefs$var <- "NA"
  coefs$beta <- "NA"
  coefs$se <- "NA"
  coefs$species <- spp 
  coefs$lifestage <- "NA"
  coefs$climate <- climate 
  coefs$min_thresholds <- min_thresholds
  coefs$max_thresholds <- max_thresholds
  coefs$optimum <- optimal_value
  coefs$start_time <- start_time
  coefs$timespan <- delta_t_total
  coefs$region <- region
  coefs$ssid_string <- ssid_string

@@

## Immature models

### Regular mixed-model
```{r}
idata <- vocc_by_sp[["imm"]]

>>>>

climate <- "do and temperature"
max_thresholds <- c(Inf, 0.75)
min_thresholds <- c(0.25, Inf)
optimal_value <- c(2, 6.5)
```

@@

optimal_string <- paste0(optimal_value, collapse = "-")
climate_string <- gsub(" ", "-", gsub("\\/", "-", tolower(climate)))
```

@@

vocc_plot <- gridExtra::grid.arrange(
  vocc_plot_temp, vocc_plot_do,
  ncol = 2,
  top = grid::textGrob(paste("do of ", optimal_value[1], "less", min_thresholds[1],"or temperature of ", optimal_value[2], "plus", max_thresholds[2], " over ", start_time, "-", start_time + delta_t_total, ""))
)

}
vocc_plot
```

@@

  for (j in seq_along(variable_names)){
  browser()
    vectors <-  filter( vectors, paste0("X",j) < (optimal_value[j] - min_thresholds[j]) )
  }

@@

if (length(vectors[ ,2]) == 0) {
  try({other_coefs <- readRDS("data/vocc-by-spp-sdmTMB-coefs.RDS")})
  coefs <- other_coefs[1,]
  coefs$var <- "NA"
  coefs$beta <- "NA"
  coefs$se <- "NA"
  coefs$species <- spp 
  coefs$lifestage <- "NA"
  coefs$climate <- climate 
  coefs$min_thresholds <- min_string
  coefs$max_thresholds <- max_string
  coefs$optimum <- optimal_string
  coefs$start_time <- start_time
  coefs$timespan <- delta_t_total
  coefs$region <- region
  coefs$ssid_string <- ssid_string

@@

## Immature models
### Regular mixed-model
